## Dataset
The dataset evaluates the obesity risk based on factors such as gender, age, number of meals, consumption of alcohol, physical activity frequency, etc. It includes 20758 observations and 18 columns

```{r}
library(tidyverse)
my_data <- read.csv("obesity_level.csv")
summary(my_data)
```

### Histogram plot
```{r}
hist(my_data$FAF, breaks = 5, xlab="Hours",
     main = "Physical Activity Frequency",
     col = "#60B8A3",
     border = "white")
```

The histogram shows the distribution of time (hours) spent on physical activity of participants.
The right-skewed distribution indicates that the majority of individuals spend between **0.0 and 1.0 hours** for physical activity.

Interestingly, the distribution shows a *secondary peak* at **1.5 to 2.0 hours**, representing a significant proportion of participants with physical activity duration.

We assume that this peak comes from the young people - those in their prime - who are ready to devote more time to physical activity.


Let's see 

```{r}
group_15_20 <- my_data %>%
  filter(FAF >= 1.5, FAF <= 2.0)

ggplot(group_15_20, aes(x = Age)) +
         geom_histogram(binwidth=5, fill ='steelblue', color='white')+
         labs(title = "Age distribution of individuals with 1.5 - 2.0 hours for physical activity",
              x = "Age", 
              y = "Count") +
         theme_minimal()
```

From the graph, we easily see that most of the participants whose age is *around 20* devote **1.5 to 2.0 hours** to physical activity.

### Statistical Calculation
**Mean of Physical Activity Frequency**
```{r}
mean_activity <- mean(my_data$FAF, na.rm = TRUE)
mean_activity

```

**Standard deviation of Physical Activity Frequency**
```{r}
sd_activity <- sd(my_data$FAF, na.rm = TRUE)
sd_activity
```

### Apply correlation 
**to detect a relationship between Age and Physical Activity Frequency**
```{r}
cor.test(my_data$Age, my_data$FAF)
```

**R-squared and p-value**
```{r}
linear_age_faf <- lm(FAF ~ Age, data = my_data)
summary(linear_age_faf)
```

**Scatter plot**
```{r}
ggplot(my_data, aes(x = Age, y = FAF)) +
  geom_point(alpha = 0.5, color = "darkgreen") +
  geom_smooth(method="lm", color='red') +
  theme_minimal() +
  labs(title = "Age vs Physical Activity Frequency",
       x = "Age",
       y = "Physical Activity Frequency")
```
     
The correlation coefficient is **-0.19**, indicating that a weak relationship. In the other hand, when age increases, the Physical Activity Frequency tends to decrease slightly. 

The **p-value < 2.2e-16**, showing that the relation is statistically significant.
The linear regression model produced **R-squared = 0.03696**, meaning Age explains only **3.7%** of the variation in Physical Activity Frequency.
Therefore, although Age has a statistically significant impact on physical activity, it is not a strong predictor, and other factors might play a much larger role.

### Second statistic test
```{r}
ggplot(my_data, aes(x = Weight)) +
  geom_histogram(binwidth = 5, fill = "orange", color = "white") +
  geom_text(stat = "bin",
            binwidth = 5,
            aes(label = ..count..),
            vjust = -0.5,
            color = "black",
            size = 3) +
  labs(title = "Weight Distribution", x = "Weight", y = "Count") +
  theme_minimal()


```

The Weight distribution is **not normal**
It spreads widely across the range of weights. It shows clear peaks around: 50, 80, 110, and 120. This indicates that weight in the dataset is not centered around a single value but forms multiple clusters

### T-test
I divided my dataset into two groups based on the variable Gender (Male vs Female) and used t-test to test for significant differences between the two groups.

```{r}
t.test(Weight ~ Gender, data = my_data)
```

The t‑test:
The mean Weight for males is **91.03**, while the mean Weight of females is **84.77**
the **p-value < 0.05**, indicating that the difference is statistically significant.
